Figures and Analysis for 2023 Manuscript

### 2023-10-17 data-raw/Manuscript2023_Workflow.Rmd
Added import and importFrom tags to functions

mvbutils::foodweb(where = asNamespace("invivoPKfit"),
                  prune = "convert_time",
                  # descendents = FALSE,
                  # ancestors = FALSE,
                  border = TRUE, cex = 1, lwd = 1.5)

@@

>>>>

mvbutils::foodweb(where = asNamespace("invivoPKfit"),
                  prune = "calc_auc",
                  # descendants = FALSE,
                  # ancestors = FALSE,
                  border = TRUE, cex = 1, lwd = 1.5)

@@

# list of all functions and methods
fm <- ls(asNamespace("invivoPKfit"))
fm <- fm[!grepl(".default", x = fm)]

pdf(file = paste0(Sys.getenv("FIG_DIR"),
              "NonDefaultFunction_Connections.pdf"),
    height = 8, width = 8)
for (i in fm) {
  mvbutils::foodweb(where = asNamespace("invivoPKfit"),
                  prune = i,
                  # descendants = FALSE,
                  # ancestors = FALSE,
                  border = TRUE, cex = 1, lwd = 1.5)
}
dev.off()
